A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-10-01 journal/experiments.tex
text fix

 Fuzzgoat (\url{https://github.com/fuzzstati0n/fuzzgoat}) is a well-known backdoored C program used to test fuzzers and other analysis tools.  It is an interesting subject to consider non-compiler fuzzer taming because it is a single program version with 4 distinct bugs with complete ground truth, and widely viewed as representative of a typical fuzzing use-case.  We ran AFL \cite{aflfuzz} for over 7 hours on the program, generating 4,244 crashing inputs (Figure \ref{aflfuzzgoat} shows a screenshot from just before we terminated the run).  AFL's internal triaging methods reduced this to a set of 38 crashes it considered distinct.  We terminated the run once it had been nearly three hours since a new distinct crash was detected.

>>>>

 Fuzzgoat (\url{https://github.com/fuzzstati0n/fuzzgoat}) is a well-known backdoored C program used to test fuzzers and other analysis tools.  It is an useful subject for demonstrating non-compiler fuzzer taming because it is a single program version with 4 distinct bugs with complete ground truth, and widely viewed as representative of a typical fuzzing use-case.  We ran AFL \cite{aflfuzz} for over 7 hours on the program, generating 4,244 crashing inputs (Figure \ref{aflfuzzgoat} shows a screenshot from just before we terminated the run).  AFL's internal triaging methods reduced this to a set of 38 crashes it considered distinct.  We terminated the run once it had been nearly three hours since a new distinct crash was detected.
